### 2003-11-24 Documentation/Manual.tex
*** empty log message ***

\part{User's manual}

\chapter*{Getting started}

@@

\part{The Experiment Definition Module (\EDM )}

\chapter{Basics: Source, Oscillation, Detection}

Here comes how a experiment is defined (what is a channel, a rule, how are they treated, ...). Splitting in source, oscillation, and detector, etc.

\chapter{Getting started: Editing existing experiments}

Here comes how to load and modify existing experiments;
also: how does the main screen work and the most important functions at exampled

\chapter{Features of the \EDM }

\section{Source properties}

\section{Oscillation properties}

\section{Detector properties}

\chapter{Creating new experiments}

Most advanced step: How to create a new experiment from scratch.

@@

\part{Reference manual}

Here comes a list of all functions and their function in alphabetical order.

@@

\begin{appendix}

\chapter{\GLOBES\ installation}

\chapter{Statistics and \GLOBES }

Here comes a statistics summary (similar to Superbeams appendix):
\bi
\item
 What $\chi^2$ is used
\item
 How channels/rules are treated
\item
 How does the flux-folding work
\item
 ...
\ei

\end{appendix}
\end{document}

>>>>

\input{part1}

@@

\input{part2}

@@

\input{part3}

@@

\input{appendix}

\end{document}
